---
title: "Creating different visualizations"
author: '[Alan Bui]'

---

---

## Adding pakages needed

For the visualizations that I will be doing all we need is ggplot2
```{r setup}
# Add your library below.

library(ggplot2)

```


## Visualization 1 - Creating histogram

For this visualization I will create a histogram of `mpg`

```{r, "Step 1"}
# Write your code below.
ggplot(mtcars, aes(mpg)) + geom_histogram(bins = 30)



```

---

## Visualization 2 -Boxplots

For this visualization I will create a boxplots of `mpg` by `cyl`. With 3 box plots: one for all cars with 4 cylinders, one for all cars with 6 cylinders, and one with all the cars with 8 cylinders.

```{r, "Step 2"}
# Write your code below.
ggplot(mtcars, aes(group=cyl, x = cyl, mpg)) + geom_boxplot()



```

---

## Visualization 3 -MultiLine chart 

For this visualization I will create a multiLine chart of `wt` on the x-axis, `mpg` for the y-axis. With a line for each `am` (i.e. two lines).

```{r, "Step 3"}
# Write your code below.
ggplot(mtcars, aes(x=wt, group=am, color = am, y=mpg)) + geom_line()



```

---

## Visualization 4 -Barchart

Barchart with the x-axis being the name of each car, and the height being `wt`.
Make sure to rotate the x-axis labels, so we can actually read the car name.

```{r, "Step 4"}
# Write your code below.
barchart <- ggplot(mtcars, aes(x=rownames(mtcars), y=wt)) + geom_bar(stat = "identity")
barchart


```